The evolution of gene expression in the term placenta of viviparous mammals

### 2015-11-21 manuscript/manuscript.Rnw
clean up some more of the OU analysis

Various OU branch models were tested against a model in which no
variation in optima among branches was allowed. The following branches
were specified in separate models to have a different optimum than all
other branches: human, bonobo, mouse, dog, cow, elephant, opossum,
human+bonobo, Euarchontoglires, and Boreoeutheria. Likelihood values
were computed for each branch model and compared to an OU model with
one optimum using likelihood ratio tests with df=1. We filtered out
genes with universally low expression levels, and included only genes
in which expression in at least one species had an
$\mathrm{FPKM}\ge10$ as described above. We corrected for multiple
testing using the false discovery rate (FDR) and calculated adjusted
$p$ values (q-values) using the Benjamini-Hochberg
correction\cite{Benjamini1995:bh_procedure}. We used the
time-calibrated phylogenetic tree of
\cite{Meredith.ea2011:ImpactsofCretaceousTerrestrial} with all species
not used in this analyses pruned.

>>>>

\DLA{The description of the OU process is terrible; it needs to be
  completely redone}

Various \ac{OU} branch models were tested against a model in which no
variation in optima ($\theta$) among branches was allowed. The
following branches were specified in separate models to have a
different optimum than all other branches: human, bonobo, mouse, dog,
cow, elephant, opossum, human+bonobo, Euarchontoglires, and
Boreoeutheria. Likelihood values were computed for each branch model
and compared to an \ac{OU} model with one optimum using likelihood
ratio tests with df=1. We filtered out genes with universally low
expression levels, and included only genes in which expression in at
least one species had an $\mathrm{FPKM}\ge10$ as described above. We
corrected for multiple testing using the \ac{FDR} and using the
Benjamini-Hochberg correction\cite{Benjamini1995:bh_procedure}. We
used the time-calibrated phylogenetic tree of
\cite{Meredith.ea2011:ImpactsofCretaceousTerrestrial} with all species
not used in this analyses pruned.
